Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-24 analysis/paper/paper.Rmd
Fixed error in code with incorrect values for defining dorsal cortex perc categories

ma_flakes_tr_with_groups <-
  ma_flakes_tr %>%
 # filter(!is.na(dorsal_cortex_perc)) %>% 
  slice(-outlier_ids) %>%
  mutate(dorsal_cortext_group =
           case_when(
             between(dorsal_cortex_perc, 0, 0) ~ "Tertiary",
             between(dorsal_cortex_perc, 1, 60) ~ "Secondary",
             between(dorsal_cortex_perc, 61, 100) ~ "Primary"
           ))

>>>>

ma_flakes_tr_with_groups <-
  ma_flakes_tr %>%
 # filter(!is.na(dorsal_cortex_perc)) %>% 
  slice(-outlier_ids) %>%
  mutate(dorsal_cortext_group =
           case_when(
             between(dorsal_cortex_perc, 0, 0) ~ "Tertiary",
             between(dorsal_cortex_perc, 1, 50) ~ "Secondary",
             between(dorsal_cortex_perc, 51, 100) ~ "Primary"
           ))
